Report

### 2020-09-17 report.Rmd
Put analysis in drake plan

```{r}
first_year_biomass <-
  full_data2 %>%
  filter(nb_year == 0) %>%
  select(station, biomass, rel_bm, log_bm, rel_log_bm) %>%
  pivot_longer(-station, names_to = "coeff", values_to = "first_year") %>%
  group_by(coeff) %>%
  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big")) %>%
  ungroup()

median_biomass <- 
  full_data2 %>%
  select(station, biomass, log_bm) %>%
  pivot_longer(-station, names_to = "coeff", values_to = "biomass") %>%
  group_by(station, coeff) %>%
  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
  ungroup()
three_first_year_biomass <-
  full_data2 %>%
  filter(nb_year <= 2) %>%
  select(station, nb_year, biomass, rel_bm, log_bm, rel_log_bm) %>%
  pivot_longer(cols = biomass:rel_log_bm, names_to = "coeff", values_to = "first_year") %>%
  group_by(station, coeff) %>%
  summarise(first_3_year = median(first_year, na.rm = TRUE)) %>%
  group_by(coeff) %>%
  mutate(com_size = ifelse(first_3_year < median(first_3_year, na.rm = TRUE), "little", "big")) %>%
  ungroup()

@@

loadd(biomass_group)
temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
  select(1:4) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(median_biomass, by = c("station", "coeff")) %>%
  left_join(biomass_group, by = c("station")) %>%
  ggplot(aes(x = bm_med, y = slope)) +
  geom_point(aes(color = com_size)) +
  facet_wrap(~coeff, scales = "free") +
  labs(x = "Median biomass (g)", y = "Slope (g.y^-1)")
```

@@

station_summary_biomass <- full_data2 %>%
  group_by(station) %>%
  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
  left_join(
    filter(three_first_year_biomass, coeff == "biomass") %>%
      select(station, first_3_year)
    , by =
    "station") %>%
  left_join(
    filter(first_year_biomass, coeff == "biomass") %>%
      select(station, first_year)
      , by =
    "station")

@@

```{r}
#grandes/petites rivières
myload(habitat_press, habitat_pressure, op_analysis, envir = environment(),
  dir = get_mypath("data"))
width_classif_mean <- habitat_press %>%
    mutate(width_classif_mean  = if_else(width_river_mean < mean(width_river_mean, na.rm = TRUE), "little",
      "big")) %>%
    select(station, width_river_mean, width_classif_mean)
habitat_press %>%
  ggplot(aes(x = width_river_mean)) +
  geom_histogram()

@@

test <- model_int$model[[3]]
car::vif(test)

@@

plot_final_model <- function (ggpred = NULL, rawdata = NULL) {
  ggpred %<>%
    as_tibble %>%
    rename(increasing = group, bm_group = facet)

@@

  p <- ggplot(ggpred, aes(x = x , y = predicted, color = bm_group)) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = bm_group), alpha =
      .1) +
    geom_line()
  p + geom_point(data = rawdata, aes(y = estimate, x = linear_slope, color =
      median_group))

@@

```{r}
model_int %<>%
  mutate(
    pred5 = map(mod5, ~ggpredict(.x,
	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2,3, 4, 6]", "inc_f", "median_group"))),
    plot = map(pred5, ~plot(.x, add.data = TRUE)),
    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = model_int$myplot, labels = model_int$coeff)
```

>>>>

```{r}
loadd(full_data2)

@@

temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
  select(1:4) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(median_biomass, by = c("station", "coeff")) %>%
  left_join(biomass_group, by = c("station")) %>%
  ggplot(aes(x = bm_med, y = slope)) +
  geom_point(aes(color = com_size)) +
  facet_wrap(~coeff, scales = "free") +
  labs(x = "Median biomass (g)", y = "Slope (g.y^-1)")
```

@@

```{r}
station_summary_biomass <- full_data2 %>%
  group_by(station) %>%
  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
  left_join(
    filter(three_first_year_biomass, coeff == "biomass") %>%
      select(station, first_3_year)
    , by =
    "station") %>%
  left_join(
    filter(first_year_biomass, coeff == "biomass") %>%
      select(station, first_year)
      , by =
    "station")

@@

```{r}
get_stream_group <- function (op_analysis_path = NULL, habitat_press_path = NULL) {
  load(file = op_analysis_path, envir = environment())
  load(file = habitat_press_path, envir = environment())

  width_classif_mean <- habitat_press %>%
    mutate(
      avg = if_else(width_river_mean < mean(width_river_mean, na.rm = TRUE),
	"little", "big"),
      median = if_else(width_river_mean < median(
	  width_river_mean, na.rm = TRUE), "little", "big")) %>%
  pivot_longer(cols = c(avg, median), names_to = "group_type", values_to =
    "group") %>%
  select(station, width_river_mean, group_type, group)

protocol_station <- op_analysis %>%
  group_by(station) %>%
  summarise(protocol_type = unique(protocol_type))

output <- width_classif_mean %>% 
  left_join(protocol_station, by = "station")

return(output)

}
#grandes/petites rivières
habitat_press %>%
  ggplot(aes(x = width_river_mean)) +
  geom_histogram()

@@

@@

plot_final_model <- function (ggpred = NULL, rawdata = NULL, facet = FALSE) {
  ggpred %<>%
    as_tibble %>%
    rename(increasing = group, median_group = facet)

@@

  if (!facet) {
  p <- ggplot(ggpred, aes(x = x , y = predicted, color = median_group)) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = median_group), alpha =
      .1) +
    geom_line()
  p + geom_point(data = rawdata, aes(y = estimate, x = linear_slope, color =
      median_group))
  } else {
    p <- ggplot(ggpred, aes(x = x , y = predicted)) +
      geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha =
	.1) +
      geom_line() 
    p + geom_point(data = rawdata, aes(y = estimate, x = linear_slope)) +
      facet_grid(cols = vars(median_group), scales = "free_x")

  }

@@

```{r}
model_int %<>%
  mutate(
    pred5 = map(mod5, ~ggpredict(.x,
	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2,3, 4, 6]", "inc_f", "median_group"))),
    pred5_df = map(pred5, as_tibble),
    plot = map(pred5, ~plot(.x, add.data = TRUE)),
    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = model_int$myplot, labels = model_int$coeff)
```

```{r}
model_int$pred5_df[[1]] %>%
  ggplot()

plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
  TRUE)
```
